Bare minimum: order theory

### 2025-09-17 BareMinima/OrderTheory/BareMinimumOrderTheory.tex
OrderTheory: added closures and intersection structures

>>>>

\section{Closures and intersection structures}

\begin{defn}
	Given a poset $(X, \leq)$ a \textbf{closure operator} is a map $c : X \to X$ that satisfies the following for all $a,b \in X$:
	\begin{enumerate}
		\item \textbf{extensive}: $a \leq c(a)$
		\item \textbf{increasing}: $a \subseteq b \implies c(a) \subseteq c(b)$
		\item \textbf{idempotent}: $c(c(a)) = c(a)$.
	\end{enumerate}
\end{defn}

\begin{defn}
	Given a set $S$, an \textbf{intersection structure}, or $\bigcap$-structure, on $S$ is a family $X \subseteq 2^{S}$ of subsets of $S$ that is closed under arbitrary intersection. That is, $\bigcap A_i \in X$ for every non-empty family $A_i \in X$. A topped intersection structure on $S$ is an intersection structure such that $S \in X$.
\end{defn}

\begin{prop}
	Let $C : 2^{S} \to 2^{S}$ be a closure operator. Then the set of closed sets $X = \{ A \subset S \, | \, C(A) = A\}$ is a topped intersection structure. Conversely, Let $X$ be a topped intersection structure, $C(A) = \bigcap \{B \in X \, | \, | A \subset B \}$ is a closure operator.
\end{prop}
